---
title: "p8105_hw6_yx2711"
author: "Yingchen Xu"
date: "2022-11-30"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)

set.seed(1)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	message = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


# Problem 1
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

# Problem 2

Upload the `homicide-data` and create a `city_state` variable and a binary outcome `resolved_status` to indicate whether the homicide is solved. Omit a few `city_state` observations. Mutate a few character variables as factor variables or numeric variable for further analysis.
```{r}
homicide = read.csv("data/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    city_state = str_c(city, ", ", state),
    resolved_status = case_when(
      disposition %in% c("Closed without arrest", "Open/No arrest") ~ "0",
      disposition == "Closed by arrest" ~ "1"
    ),
    resolved_status = as.factor(resolved_status),
    victim_age = as.numeric(victim_age),
    victim_race = as.factor(victim_race),
    victim_sex = as.factor(victim_sex)
  ) %>% 
  filter(
    !city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")
  ) %>% 
  drop_na(victim_age)
```


Filter the analysis for whom in `Baltimore, MD` and `victim_race` is `White` or `Black`.
Fit logistic regression using `glm`.
```{r}
homicide_analysis = homicide %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state == "Baltimore, MD")

fit_logistic = homicide_analysis %>% 
  glm(resolved_status ~ victim_age + victim_sex + victim_race, family = binomial(), data = .)
  
fit_logistic = fit_logistic %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    LB = exp(estimate - 1.96*std.error),
    UB = exp(estimate + 1.96*std.error)
    ) %>% 
  select(term, estimate, OR, LB, UB) 

fit_logistic %>% 
  knitr::kable(digits = 3)
```

After adjusting for victim age and victim race, the odds ratio for solving homicides comparing male victims to female victims is `r fit_logistic %>% filter(term == "victim_sexMale") %>% select(OR)`. The 95% confidence interval for the adjusted odds ratio is (`r fit_logistic %>% filter(term == "victim_sexMale") %>% select(LB)`, `r fit_logistic %>% filter(term == "victim_sexMale") %>% select(UB)`).

Interpretation: The odds for solving homicides for male victims is 0.426 times the odds for solving homicides for female victims. We are 95% confidence that the true odds ratio lies between 0.325 and	0.558.


# Problem 3
```{r}
birthweight = read.csv("data/birthweight.csv") %>% 
  janitor::clean_names()
```

